---
title       : Developing Data Products - Course Project
subtitle    : Visualizing Trends in Bonds Issuances in East Asian Countries
author      : Justin Wong
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What does the Application do?

1. Draws data from AsianBondsOnline.
2. Cleans the data.
3. Formats the data and plots a neat graph based on the user's inputs.

--- .class #id 

## Why is this application useful?

1. The data on the AsianBondsOnline website is not very well formatted. Further, the data is not actually in xls format despite it being downloaded as such.
2. The data is best read in html format. This is what this application helps to do.
3. Furthermore, the data is not very clean. This application helps to clean it.

## What does the user need to do?

1. Simply select the Country, Entity type and Currency of choice.
2. Enter submit.
2. Viola, the application will draw the data and plot automatically.

--- .class #id

## Example of the code used to download the data.

```{r echo=FALSE}
library(ggplot2)
library(plyr)
library(zoo)
library(XML)
library(reshape2)
```
```{r}
dat<-readHTMLTable("http://asianbondsonline.adb.org/spreadsheets/RG-LCY_Bond_Market_USD.xls")
dat<-data.frame(dat)
names(dat)<-gsub("NULL.","",names(dat))

for (i in 3:ncol(dat)) {
        dat[,i]<-as.character(dat[,i])
        dat[,i]<-as.numeric(dat[,i])
}

dat$Date<-as.Date(as.yearmon(dat$Date))

dat<-melt(dat,id.vars=c("Date","Market"),variable.name="Entity")

dat$Currency<-rep("USD",nrow(dat))

dat$Currency[grep("LCY",dat$Entity)]<-"LCY"

dat$Entity<-as.character(dat$Entity)

dat$Entity[grep("Government",dat$Entity)]<-"Government"

dat$Entity[grep("Corporate",dat$Entity)]<-"Corporate"

dat$Entity[grep("Total",dat$Entity)]<-"Total"

summary(dat)
```

--- .class #id

## Credits

1. AsianBondsOnline for the easy access to the data. The data can be found at this [link](http://asianbondsonline.adb.org/regional/data/bondmarket.php?code=LCY_Bond_Market_USD)




